Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-11-03 design.tex
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

Platform is the cradle of the ecosystem and the incubator for manufacturing service, with the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order. Most recent researchers e.g. Wu et al. \cite{Wu2013}, describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
In this mode, individual executes activities that interact with others depicted by object flow (full lines) and information flow (dashed lines). A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part and we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:scheduleChart}, \textbf{inactive} when this part is just assigned to the job queue. Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.

>>>>

Platform is the cradle of the ecosystem and the incubator for manufacturing service, demander and provider make decisions through it to arrange the resources for task performance. Most recent researchers e.g. Wu et al. \cite{Wu2013}, described this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
In original mode, entities interact with each others is depicted by object flow (full lines) and information flow (dashed lines). A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part and we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:scheduleChart}, \textbf{inactive} when this part is just assigned to the job queue. Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.

### 2016-11-03 discussion.tex
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

% !TEX root = Eco-Model.tex
\section{Conclusions, Limitations, and Future Research} % (fold)
\label{sec:contributions_limitations_and_future_research}
(This part is too short, not cover everything!!!!)

In the extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate. The combine of incubation and metabolism mode makes the maintenance of platform much easier.
However, we only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions. The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.
% section contributions_limitations_and_future_research (end)

\section{Acknowledgments} % (fold)
\label{sec:acknowledgments}
This work is supported by the National Natural Science Foundation of China (No. 71571161), the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101), and the Fund of Key Lab of AMT of Zhejiang Province (No. 2015QN01). 
% section acknowledgments (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Conclusions, Limitations, and Future Research} % (fold)
\label{sec:contributions_limitations_and_future_research}
The operation modes proposed in this paper represented ways to the arrangement of resource to handle the environmental burden, and the $RE$ value showed in \autoref{tab:averagevalue}, reduced wast and idle of manufacturing resources have partially achieved, if Mode 11 was selected as the reference standard, since this value means the amount of task that can be manufactured per unit of resource.

As for extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate. The combine of incubation and metabolism mode turns out to be a ideal maintenance pattern for operating.

However, we only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions. The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.
% section contributions_limitations_and_future_research (end)

\section{Acknowledgments} % (fold)
\label{sec:acknowledgments}
This work is supported by the National Natural Science Foundation of China (No. 71571161), the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101), and the Fund of Key Lab of AMT of Zhejiang Province (No. 2015QN01). The authors also gratefully acknowledge the insightful comments from anonymous reviewers which have helped to
improve significantly on the earlier version of this paper.
% section acknowledgments (end)

### 2016-11-03 result.tex
ready for merge
add result figure in figures
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22.
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ means that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.eps}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
% subsubsection result_and_analysis (end)

>>>>

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue}, meaning of new most symbols are defined as the title of all the plots in \autoref{fig:out}, $RE$ denotes the resource efficiency determined by \autoref{eq:re}
\begin{equation}
  RE = \frac{\bar N_F}{\bar N_R} \label{eq:re}
\end{equation}
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lcccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$ & $RE$\\
    \midrule
    Mode 11 & 1159.360 &  1644.201 &  1177.601 &  2053.727 &  8.388 & 0.801\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016 & 1.904\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174 & 1.658\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057 & 0.516\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251} & 1.259\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652} & 0.785\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22.
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ means that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{figures/out_new.pdf}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
% subsubsection result_and_analysis (end)

### 2016-11-03 review.tex
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

% !TEX root = Eco-Model.tex
\section{Background and literatures} % (fold)
\label{sec:literature_review}
\subsection{Background} % (fold)
\label{sub:background}
1. environmental issues

In cloud manufacturing context, provider entity publishes manufacturing resources, demander entity publishes manufacturing tasks, platform arranges these resources properly to perform the tasks. As one object in research scope of this paper, the mode to generate manufacturing service, which is an arrangement of resources, is discussed along with another object that the mode to keep resource in high quality instead of low quality.

>>>>

% !TEX root = Eco-Model.tex
\section{Background and literatures} % (fold)
\label{sec:literature_review}
\subsection{Background} % (fold)
\label{sub:background}
Resource consumption in manufacturing activities is inevitable, waste and idle of these resources  are pervasive in existing manufacturing systems \cite{Smith2012}. Effective utilization of resources and resource productivity driven manufacturing innovation is one key consideration to handle the environmental burden \cite{Dornfeld2014,Li2012}.

In cloud manufacturing context, provider entity publishes manufacturing resources, demander entity publishes manufacturing tasks, platform arranges these resources properly to perform the tasks.
In scope are the mode to generate manufacturing service, which is an arrangement of resources, and the mode to keep resource in high quality instead of low quality.
